Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-03 doc/PRF2022/PRF_main.tex
worked on final points

\usepackage{todonotes}
\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{tabularx}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The Janus particles are suspended in a viscous solvent. The particles
are disks of radius $c$, center $\aa_i$, and orientation $\theta_i$
relative to the horizontal axis, where $i = 1, \ldots, N_b$ and $N_b$ is
the number of particles. The domain $\Omega(t) \subset \mathbb{R}^2$ is
the solvent phase and $t$ is time. The boundary of $\Omega$ is
$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
is the boundary of Janus particle $i$. Assuming inertial terms are
negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{align}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

@@

Once \eqref{eq:stokes}--\eqref{eq:force} have been solved, the
velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} update the
particle positions and orientations.  We use the parameters $\mu = 1$
mPa s, $\gamma = 4$ pN nm$^{-1}$, $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$
pN, and $\rho_0 = 0.5$ nm.  These values give a characteristic time $1$
ns and characteristic length $1$ nm.

@@

For the velocity, we use the representation
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DDD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
where $\eeta$ is a vector-valued density function and
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{(\xx - \yy) \cdot \nnu_\yy}{|\xx - \yy|^2}
    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
    \cdot \eeta(\yy)\, \dif s_\yy.
\end{align}
The Stokeslets and Rotlets are
\begin{align}
  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
\end{align}
respectively, where $\rr = \xx - \aa_i$~\cite{pow-mir1987}. Letting
$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
condition of the double layer potential~\cite{poz1992}, and imposing the
no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
$\eeta$, translational velocity $\vv_i$, and rotational velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DDD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:vel_BLM_rep2}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)--(d) show
  the configurations with streamlines of a vesicle is in a TG flow at
  $t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the relative enclosed
  area $A/A_0$ calculated from the bilayer midplane decreases over time.
  The inset shows the relative length $l/l_0$ 
  which remains nearly constant with small magnitude of oscillations
  The inset and main panel have the same  horizontal axis.}
\end{figure}

>>>>

%\usepackage{showkeys}
\usepackage{todonotes}
\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{tabularx}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The Janus particles are suspended in a viscous solvent. The particles
are disks of radius $c$, center $\aa_i$, and orientation $\theta_i$
relative to the horizontal axis, where $i = 1, \ldots, N_b$ and $N_b$ is
the number of particles. The domain $\Omega(t) \subset \mathbb{R}^2$ is
the solvent phase and $t$ is time. The boundary of $\Omega$ is
$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
is the boundary of Janus particle $i$. Assuming inertial terms are
negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
\label{eq:stokesMass}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokesFarfield}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{align}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

@@

To perform a single time step, we first solve for the HAP by
solving~\eqref{eq:SL}--\eqref{eq:SLbc}, and then compute the force and
torque~\eqref{eq:FandTdef}. Then the Stokes
equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield} are solved, and
the force-free and torque-free conditions are used to compute the rigid
body motion~\eqref{eq:rigid-vel}.
Once~\eqref{eq:stokes}--\eqref{eq:force} have been solved, the
velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} update the
particle positions and orientations.  We use the parameters $\mu = 1$
mPa s, $\gamma = 4$ pN nm$^{-1}$, $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$
pN, and $\rho_0 = 0.5$ nm.  These values give a characteristic time $1$
ns and characteristic length $1$ nm.

@@

For the velocity, we use the representation
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DDD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
where $\eeta$ is a vector-valued density function and
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{(\xx - \yy) \cdot \nnu_\yy}{|\xx - \yy|^2}
    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
    \cdot \eeta(\yy)\, \dif s_\yy.
\end{align}
The Stokeslets and Rotlets are
\begin{align}
  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
\end{align}
respectively, where $\rr = \xx - \aa_i$~\cite{pow-mir1987}. Letting
$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
condition of the double layer potential~\cite{poz1992}, and imposing the
no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
$\eeta$, translational velocity $\vv_i$, and rotational velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DDD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:vel_BLM_rep2}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.
Equation~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} does have a
unique solution, but we note that alternative full-rank layer potential
representations for rigid body motions are possible~\cite{rac-gre2016,
cor-gre-rac-vee2017}.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)--(d) show
  the configurations with streamlines of a vesicle is in a TG flow at
  $t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the
  relative enclosed area $A/A_0$ calculated from the bilayer midplane
  decreases over time. The inset shows the relative length $l/l_0$ which
  remains nearly constant with small magnitude of oscillations. The
  inset and main panel have the same horizontal axis.}
\end{figure}
